% Ubah judul dan label berikut sesuai dengan yang diinginkan.
\section{Conclusion}
\label{sec:conclusion}

% Ubah paragraf-paragraf pada bagian ini sesuai dengan yang diinginkan.

Based on the test results that have been carried out and analyzed in the previous chapter, the following conclusions are obtained:

\begin{enumerate}

  \item This research successfully developed an eye gesture-based wheelchair control system using MediaPipe and Intel NUC. The system is able to recognize eye movements with a high level of accuracy and translate them into commands to control the wheelchair.

  \item The classification model used shows excellent performance based on the confusion matrix evaluation results. The model can recognize various eye movements quickly and consistently. Ensuring that the model can reliably recognize eye movements with high accuracy.

  \item At distances of 30 and 50 cm, the model has the highest accuracy of 100\%. The model shows that the further away the eye is from the camera, the lower the accuracy, especially in the “Forward” and “Backward” classes.

  \item The model performed reasonably well across a wide range of lighting levels, with the highest accuracy of 100\% at 131 Lux illumination. This shows that light has a significant influence on the accuracy of the model, with increased accuracy at higher illumination. 

  \item The FPS performance test results show that the system can maintain a more stable and faster FPS on the Laptop. This is due to the difference in specifications, where the laptop uses a GPU, while the NUC uses a CPU.
  
  \item The average response time of the motors for the “Right,” “Left,” and “Backward” commands is below 0.25 seconds, indicating a responsive system. Whereas for the “Forward” command it is 0.4337 seconds and for the “Stop” command it is 0.4318, indicating a higher response time as the command takes longer to execute.
  
  \item The wheelchair motor has consistent output times in each command class, with relatively narrow variability with standard deviation values for the “Right” class of 0.408, “Left” class of 0.371, “Forward” class of 0.117, “Backward” class of 0.156, and “Stop” class of 0.361. Among all the command classes, the "Forward" class has the most stable value.

\end{enumerate}